Title

### 2024-05-31 paper/main.tex
Updates

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset.

To perform any causal effect identification or estimation using Directed
Acyclic Graphs (DAGs) or Structural Equation Models (SEMs), researchers need to
first construct a causal structure. This process of constructing the casual
structure from data is known as \emph{causal discovery}. In the field of DAGs,
a lot of effort has been put on developing automated algorithms that can
construct these DAGs from data. These algorithm takes different approaches to
causal discovery such as Constraint-based algorithms such as PC and Fast Causal
Infenrece (FCI) where the algorithm tries to match the conditional
independences in the data to the ones impled by the model, score-based methods
such as Hill-Climb Search, Greedy Equivalence Search (GES)  where the algorithm
tries to find a model that has the best score given some scoring metric, and
continuous optimization where the problem is formulated as a constrained
optimization problem such as No Tears.

Even though we have various algorithms for doing casual discovery, yet
researchers in applied fields prefer to construct these DAGs manually based on
their domain knowledge. We hypothesize the following two reasons for low
adaption of these methods in applied sciences:

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often make
		very obvious mistakes, making it harder for the user to trust
		them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of
		these algorithms on our dataset.
\end{enumerate}

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data and potentially modifying 
them for a better fit before using them for making any inference. Both global
and local tests for testing the fit of these models are available. However, when
the fit fails, we don't have a procedure to modify these models.

In the field of Structural Equation Models (SEMs), models are also typically
constructed by hand. Researchers typically come up with an initial model, which
then they use the data and expert knowledge to make modifications to. This
process is known as \emph{Specification Search}. One of the common ways to do
this is through \emph{modification indices} where a global fit of the model is
measured with different modification to the model. Utilizing expert knowledge
to select the appropriate modification that gives the maximum improvement to
the global fit.

@@

\subsection{Effect size Measures}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.

>>>>

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset. Causal discovery techniques are
used typically to understand and estimate causal effects between variables. In
the To perform any causal effect estimation using Directed Acyclic Graphs
(DAGs) or Structural Equation Models (SEMs), researchers need to first
construct a causal structure. In the field of DAGs, a lot of attention has been
put on developing automated algorithms that can construct these DAGs from data.
These algorithm takes different approaches to causal discovery such as
constraint-based algorithms such as PC and Fast Causal Infenrece (FCI) where
the algorithm tries to match the conditional independences in the data to the
ones impled by the model, score-based methods such as Hill-Climb Search, Greedy
Equivalence Search (GES)  where the algorithm tries to find a model that has
the best score given some scoring metric, and continuous optimization where the
problem is formulated as a constrained optimization problem such as No Tears, and
some hybrid approaches.

Even though we have various algorithms for casual discovery, the adaption of these
algorithms in applied fields remain limited. In these applied fields, researchers 
typically prefer to construct these DAGs manually based on their domain knowledge.
We hypothesize that this preference towards manual DAG construction stems from the 
following difficulties in applying these methods to real dataset.

\begin{enumerate}
	\item Algorithms output Markov Equivalence Class (MEC): Using observational
		data, any causal discovery algorithm can only output the MEC.
		MEC do not have all the edges oriented and to do further
		hypothesis testing or causal effect estimation, researchers
		typically have to rely on domain expertise to orient the
		remaining edges in the MEC.
	\item Difficulties in choosing an algorithm: To use any of these algorithms on 
		any practical dataset, users need to make a lot of choices. For
		example, for using constraint-based method, users need to
		choose a suitable condtional independence (CI) test, and
		hyperparameters for these tests. Similarly for score-based
		methods users need to choose the scoring metrics and their
		hyperparameters. Moreover, for practical implementation with
		reasonable runtime, users also need to choose the algorithm
		hyperparameters such as maximum number of conditioning
		variables to consider, max indegree of variables in the model. With
		no easy guides or method to evaluate these choices, it can be difficult.
	\item Lack of trust: Most of these automated algorithms can make very obvious 
		mistakes. Typically users have to test the outputs of the models and 
		manually make corrections to the output to get a usable model.
		This can lead to researchers not trusting these algorithms.
\end{enumerate}

On the other hand, in the field of Structural Equation Models (SEMs), models
are also typically constructed by hand. And a lot of focus has been put on
developing tools to help researchers in constructing these models. Researchers
typically come up with an initial model, which then they use the data and
expert knowledge to make modifications to. This process is commonly known as
\emph{Specification Search}. These tools can then be used to guide the
researchers in suggesting best ways to modify the model. For example,
\emph{modification indices} take the initial drawn model, and make all possible
modifications to the model to check which modification improves the model fit
the best. Based on this information, the researcher can make modifications to
the model and reiterate this process till they get something that they are
satisfied with.

In the case of DAGs, global testing methodology does exist such as Shipley
test, that can combine local structure tests into a single p-value test.
However, this does not give us a way to make modifications to our model. A
possible way to do this by using check which of these local tests are violated
based on the

In the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data and potentially modifying 
them for a better fit before using them for making any inference. Both global
and local tests for testing the fit of these models are available. However, when
the fit fails, we don't have a procedure to modify these models.

@@

\subsection{Association Measures}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.
